---
title: "Godly Governance"
subtitle: "Examining Support for Religious Governance <br> in Arab Muslim Majority Countries"
author: 'Fabio Votta <br><br> <a href="http://github.com/favstats"><i class="fa fa-github fa-fw"></i>&nbsp; favstats</a><br> <a href="https://twitter.com/FabioFavusMaxim"> <i class="fa fa-twitter fa-fw"></i>&nbsp; @FabioFavusMaxim</a><br> <a href="mailto:fabio.votta@gmail.com"><i class="fa fa-paper-plane fa-fw"></i>&nbsp; fabio.votta@gmail.com</a><br>'
date: "2018-28-05 <br><br> Slides available at <a href='godly-governance.netlify.com'>https://godly-governance.netlify.com/ </a>"
output: 
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      highlightLanguage: r
    includes:
      in_header: header.html      
    countIncrementalSlides: false
    css: xaringan-themer.css
---



    

```{r xaringan-themer, include = FALSE}
library(xaringanthemer)
# mono_accent(base_color = "#252525", link_color	= "rgb(198, 219, 239)")
```

<style>
.onehundredtwenty {
  font-size: 120%;
   }

<style>
.ninety {
  font-size: 90%;
   }

.eightyfive {
  font-size: 85%;
   }
   
.eighty {
  font-size: 80%;
   }
   
.seventyfive {
  font-size: 75%;
   }
   
.seventy {
  font-size: 70%;
   }
</style>


```{r setup, echo = F, include=F}
# include=FALSE
options(htmltools.dir.version = FALSE)

pacman::p_load(tidyverse, xaringan)

knitr::opts_chunk$set(echo = F, warning = F, error = F, message = F)

```


<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

.onehundredtwenty[

Research Question:

> What role does religiosity play in support for religious governance? 

]



---

## Outline

.onehundredtwenty[

1. Theoreteical Framework
2. Data & Methodology
3. Challenges
4. Analysis & Results
5. Conclusions & Future Research

]


---

class: inverse, center, middle

## Theoretical Link between <br> Deliberation and Regime Legitimacy 


---

## Theory

+ Central claim of deliberative theory: 
    + making it possible to arrive at (more) legitimate desicions


--
+ Conceptualization of legitimacy as regime support 


--
+ General assumption: Deliberative qualities of a political system increase support from its citizens


--
+ *Authoritarian deliberation*: Might decrease support due to increasing democratic capabilites



---

class: inverse, center, middle


## Data & Methodology


---

#### Data & Methodology

**Individual-Level Data**
+ Merging of the following datasets: 
  + Afrobarometer Survey, Round 5 and Round 6 (data from 2011-2015)  
  + Asian Barometer Survey, Wave 3 and Wave 4 (2010-2015) 
  + AmericasBarometer (2010-2014) 
  + European Social Survey, Round 6 (2012) 
  + Latinobarómetro (2015) 
  + World Values Survey (2010-2014)

+ In total 316,938 individual cases in 119 Countries
  + weighted to same sample size (=1000)


--

**Country-Level Data**
+ "Varieties of Democracy"-Dataset: Deliberative Component Index
+ Control variables come from V-Dem and the QoG-Dataset
+ Lagging of Independent Variables (Averaging from 2000 - 2010)

---

#### Data & Methodology

.ninetyfive[

+ Control Variables
    + Micro Level
        + Age
        + Sex (Male/Female)
        + Financial Security
        + Education
        + Employment (0/1)
    + Macro Level
        + Polity/FH
        + Democracy (0/1)
        + Autocracy (0/1)
        + logged GDP per capita
        + logged Population
        + Life Expectancy
        + Urban Pop. Ratio
    + Survey dummies
        + WVS, Afrobarometer, Latinobarometro, Americasbarometer, Asianbarometer, ESS
        
]

---


## Operationalization of Regime Support

Three types of traditional political branches
+ executive (political leadership)
+ judicial and legal system (courts and police)
+ legislation (parliament) 



---

## Deliberative Component Index (DCI)?

+ short description?
+ Table with five components?


---

## World Maps

---

class: inverse, center, middle


## Challenges

---

## Challenges

*Two major challenges emerged:*

+ Colinearity between Deliberation indicators and Democracy Measures

--

+ Possibly biased self-reported regime support 

--

<br>

#### Multicolinearity issue



---

#### Correlation between DCI and Polity/FH





---


#### Possibly biased self-reported Regime Support 



---

#### Correlation between Regime Support and Discussion Suppression 



---

#### Weighting of Regime Support



---

class: inverse, center, middle


## Analysis & Results

---

## Analysis

+ Multilevel Models
    + In total 91 seperate models
    + DVs: Regime Support (No, Low, High Bias)
    + Main IVs: All six Deliberation indicators
    

---

## Results


---

### Model Comparisons -Just Polity/FH Models vs. Complete Models


---

class: inverse, center, middle

## Conclusions & Future Research

---

## Conclusions & Future Research

* No simple answer to research question
 + deliberation seems to have a positive effect on regime support in democracies
 + less robust and ambiguous results for non-democracies and complete sample
    
    
* Presumably biased regime support
 + should be taken into account 
 + possible remedies? (e.g. weighting procedures, survey design)

* Validity of the DCI
    + more sensitive approaches to measure deliberation on the country level are neccessary
    + nevertheless interesting differences regarding the subsamples

---

class: inverse, center, middle


## Thanks for Listening!

Full Paper: <a href='https://www.academia.edu/36656020/Deliberation_Across_the_World_A_Cross-National_Examination_of_the_Link_Between_Deliberation_and_Regime_Legitimacy'>Deliberation Across the World</a>

Slides: <a href='deliberation-and-legitimacy.netlify.com'>https://deliberation-and-legitimacy.netlify.com </a>

Online Appendix can be found <a href='https://favstats.github.io/delib_mod_database'>here</a>

Code and Data on <a href='https://github.com/favstats/paper_delib'>GitHub</a>


---

## References




---

class: inverse, center, middle

## Appendix

---


#### Operationalization of Regime Support


---

### Maps - Deliberation

---

### Maps - Regime Support

---

### Coefficent Plots - Complete Sample

---

### Coefficent Plots - Democracy Sample

---

### Coefficent Plots - Non-Democracy Sample

---



### Model Comparisons - Just Control Models vs. Just Deliberation Models


---

### Model Comparisons - Complete Sample



---

### Model Comparisons - Democracy Sample



---

### Model Comparisons - Non-Democracy Sample





